On the effects of partying on next-day sports performance

### 2017-07-05 writing/draft.tex
Added a couple more anecdotal references.

We plot a heatmap which displays the logged count of co-occurences between last game
location and current game location, split by home-and-away games.
Our takeaway from this figure is that indeed there is some correlation between last game location
and next day opponent (more so when both are away games,  
and in particular this is true for west coast teams). We hypothesize that
this is due to practical limitations on flight schedules. E.g. if a team is unwilling to take a red-eye
flight, then there is little hope to play an evening west coast game and make it to the east coast for a game the very next day;
the same is \emph{not true} when flying from east to west, in which case a morning flight is reasonable.
The fact that there is some correlation between last game location and next day opponent, even if only in west coast cities, increases the motivation for conditioning on spread, which may help account for systematic biases to the extent that some of these next-day opponents are particularly (not) skilled.

@@

% mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   party placebo & 0.072 \\    & (0.082) \\    & \\   lag changes in posession & 0.00001 \\    & (0.002) \\    & \\   logged travel distance & $-$0.005 \\    & (0.026) \\    & \\   east-west travel direction & $-$0.099 \\    & (0.232) \\    & \\   number hours rest time & 0.001$^{*}$ \\    & (0.001) \\    & \\   time of game during day & 0.001 \\    & (0.013) \\    & \\   home team effect & $-$0.009 \\    & (0.043) \\    & \\   logged travel distance * east-west & 0.015 \\    & (0.036) \\    & \\   Constant & $-$0.070 \\    & (0.378) \\    & \\  \hline \\[-1.8ex]  Observations & 9,823 \\  Log Likelihood & $-$6,806.702 \\  Akaike Inf. Crit. & 13,631.400 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}  
\subsection{Possible confounders or potential issues}

>>>>

We plot a heatmap which displays the logged count of co-occurences between last game
location and current game location, split by home-and-away games.
Our takeaway from this figure is that indeed there is some correlation between last game location
and next day opponent (more so when both are away games,  
and in particular this is true for west coast teams). We hypothesize that
this is due to practical limitations on flight schedules. E.g. if a team is unwilling to take a red-eye
flight, then there is little hope to play an evening west coast game and make it to the east coast for a game the very next day;
the same is \emph{not true} when flying from east to west, in which case a morning flight is reasonable.

The fact that there is some correlation between last game location and next day opponent, even if only in west coast cities, increases the motivation for conditioning on spread, which may help account for systematic biases to the extent that some of these next-day opponents are particularly (not) skilled. 
In fact, using point-spread data we may weaken our assumption: we only need
likelihood of meeting the spread to be uncorrelated with last game location
in order to have identification in our variable of interest.

@@

% mp
\begin{tabular}{@{\extracolsep{5pt}}lc}  \\[-1.8ex]\hline  \hline \\[-1.8ex]   & \multicolumn{1}{c}{\textit{Dependent variable:}} \\  \cline{2-2}  \\[-1.8ex] & Meet the Spread (NBA) \\  \hline \\[-1.8ex]   Party placebo & 0.072 \\    & (0.082) \\    & \\   Lag changes in posession & 0.00001 \\    & (0.002) \\    & \\   Logged travel distance & $-$0.005 \\    & (0.026) \\    & \\   East-west travel direction & $-$0.099 \\    & (0.231) \\    & \\   Number hours rest time & 0.001$^{*}$ \\    & (0.001) \\    & \\   Time of game during day & 0.001 \\    & (0.013) \\    & \\   Home team effect & $-$0.009 \\    & (0.043) \\    & \\   Logged travel distance * east-west & 0.015 \\    & (0.036) \\    & \\   Constant & $-$0.069 \\    & (0.378) \\    & \\  \hline \\[-1.8ex]  Observations & 9,823 \\  Log Likelihood & $-$6,806.701 \\  Akaike Inf. Crit. & 13,631.400 \\  \hline  \hline \\[-1.8ex]  \textit{Note:}  & \multicolumn{1}{r}{$^{*}$p$<$0.1; $^{**}$p$<$0.05; $^{***}$p$<$0.01} \\  \end{tabular}

\subsection{Possible confounders or potential issues}
